ZPY: Open Source Synthetic Data for Computer Vision

### 2021-06-24 docs/paper/paper.tex
workflow section

The synthetic data workflow can be broadly divided into three categories: simulation design, generation, and tuning.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{workflow.png}
	\caption{The Synthetic Data Workflow allows for iteration of the dataset.}
	\label{fig:workflow}
\end{figure}

@@

The full workflow for synthetic data can be reduced into four key steps: \emph{Design} \ref{sec:worflowdesign}, \emph{Generation} \ref{sec:generation}, \emph{Evaluation} \ref{sec:evaluation}, \emph{Iteration} \ref{sec:iteration}. The synthetic data workflow is similar to the workflow when using collected data, with the key exception that it allows for iteration on the dataset itself \ref{fig:workflow}.

\subsection{Design}
\label{sec:worflowdesign}

The first step in the syntehtic data workflow is to design and create the sim, short for simulation. A sim is a collection of assets controlled through a single script. The run() function in the script acts as the point of entry for any generation process. Relevant parameters are put as kwargs in the run() function, which allows configuration through gin-config, a python package for configuration of python libraries.

\subsection{Generation}
\label{sec:generation}

Datasets are rendered frame by frame. Separate rendering passes are required for segmentation and color images.

Datasets can be rendered locally directly inside the Blender GUI. This allows for easy debugging when developing a sim. Once it is working locally, a sim can be exported into a zip file which will contain all the asset dependencies required. This zip file can be uploaded to the cloud with any of the user interfaces described in \ref{sec:userinterfaces}.

Dataset are then generated in the cloud \ref{sec:cloudbackend}.

We provide workflows for packaging several smaller datasets into a single larger dataset, as well as sorting individual datapoints into test, train, and validation buckets.

\subsection{Evaluation}
\label{sec:evaluation}

Sweeping over dataset hyperparameters (much like sweeping over model architecture parameters)

Fine-tuning pre-trained models as a proxy for dataset performance

@@

Least understood part of developing with synthetic data

The promise of AutoML for datasets

>>>>

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{workflow.png}
	\caption{The synthetic data workflow allows for iteration of the dataset, unlike the manual data workflow, which depends on data collection.}
	\label{fig:workflow}
\end{figure}

@@

The full workflow for synthetic data can be reduced into four key steps: \emph{Simulation Creation} \ref{sec:worflowsimcreation}, \emph{Dataset Generation} \ref{sec:generation}, \emph{Model Evaluation} \ref{sec:evaluation}, \emph{Iteration} \ref{sec:iteration}. The synthetic data workflow is similar to the workflow when using collected data, with the key exception that it allows for iteration on the dataset itself \ref{fig:workflow}.

\subsection{Simulation Creation}
\label{sec:worflowsimcreation}

The first step in the syntehtic data workflow is to design and create the \emph{sim}, short for simulation. A sim is a collection of 3D assets controlled at runtime through a single script called the \emph{run script}. The run script defines a function \lstinline{run(*)}, which acts as the point of entry for any generation process. Important parameters that configure the behavior of the run script are defined as kwargs, short for keyword arguments, in the \lstinline{run(*)} function. These kwargs allow configuration of the simulation through gin-config, a python package for configuration of python libraries \citep{ginconfig}.

The run script can be broken into two sections: the \emph{setup} and the \emph{loop}. The setup is executed first and typically only once. Setup can include code for creating categories, loading assets, and storing the pose of virtual objects in the scene. The loop, named after the \lstinline{for} loop python pattern, is repeated for some number of frames. Each frame can include code for jittering, saving annotations, and rendering images.

\begin{lstlisting}[language=Python,caption={Basic structure of a run script.},label={lst:setuploop}]
def run\left(  
	kwarg_1 : bool = False,
\right)):
	# Setup Code
	for frame in zpy.blender.step():
		# Loop Code
\end{lstlisting}

\subsection{Dataset Generation}
\label{sec:generation}

Once a sim has been created it can be used to generate data. There is no constraint on the type of data a sim can generate, though images are the most common. Each frame of the loop in a run script will render out color and segmentation images. Datasets can be generated locally directly inside the Blender GUI through the zpy Blender AddOn \ref{sec:blenderaddon}. This makes sim development possible by making the local debuggin loop faster. Once a sim is properly generating data locally, it can be exported and uploaded to the cloud backend. Exporting is done through the Blender AddOn, and will create a zip file which contains all the asset dependencies required for sim execution. The exported sim can be uploaded to the cloud backend through any of the user interfaces described in \ref{sec:userinterfaces}.

Datasets can be generated in parallel, with multiple cloud machines running concurrent instances of the same sim. Each machine is given a different random seed, resulting in a unique dataset. The resulting collection of smaller datasets can be packaged into into a single larger dataset, making it easier for a machine learning practitioner to download and work with the dataset. Additional workflows are provided for sorting individual datapoints into test, train, and validation buckets.

\subsection{Model Evaluation}
\label{sec:evaluation}

Machine learning models are trained on a dataset for some time, and periodically evaluated on validation and test datasets. Model performance in computer vision can be measured in a variety of ways, such as precision and recall, or more aggregate metrics like mean average precision (mAP). Picking the right metric is problem specific and usually comes down to which type of failure is the most important: false positives or false negatives.

@@

Those familiar with machine learning model development are aware of \emph{hyperparameters}: parameters whose value are used to control the learning process. Common examples of these include batch size, learning rate, and training epochs. These parameters, unlike the weights inside the model with are learned through training, must be set by the experiment designer. In practice, a human will use their intuition to decide upon a set or range of possible values for these hyperparameters, and then sweep over the possible hyperparameter space to find the best values for a given problem. This process, known as tuning, can have a high cost in engineering time and compute footprint. A technique known as AutoML has improved tuning by significantly reducing the engineering time cost. In AutoML, an automated process will tune these hyperparameters over time by trying different permutations, usually guided through a single heuristic score.

The kwargs of the run function in a sim are effectively additional hyperparameters that can also be tuned. The human designer of the sim can define plausible values and ranges for these sim hyperparameters, and then use an AutoML-like system to discover the values that result in the best model. This presents a unique opportunity in the machine learning workflow, where the dataset used to train a model is no longer static, and can be tuned and improved over time.
